Import and Tidy ADFG Supplied Location and Haul-out Data

### 2023-03-01 data_raw/adfg/adfg_tidydata.Rmd
troubleshoot/fix labeling of SPOT/SPLASH
there were two deployments ("EB16KKA-110597","PL17SCM-158422") for which the timeline data incorrectly labeled both tags as SPOT. This should fix this issue.

```{r}
adfg_deployments <- readr::read_csv('ADFG_SealDeploymentTable3.csv')
adfg_deployments_new <- readr::read_csv('ADFG_SealDeploymentTable_NewRecords.csv')
```

@@

adfg_deployments <- readr::read_csv('ADFG_SealDeploymentTable3.csv',
                                    col_types = adfg_deploy_cols) %>% 
  mutate(DateTagged = parse_datetime(DateTagged,format = "%m/%d/%Y %H:%M")) %>% 
  dplyr::mutate(DateTagged = lubridate::force_tz(DateTagged, 
                                                 'America/Anchorage')) %>% 
  dplyr::mutate(DateTagged = lubridate::as_datetime(DateTagged, 
                                                tz = 'America/Anchorage'))

@@

adfg_deployments_new <- readr::read_csv('ADFG_SealDeploymentTable_NewRecords.csv',
                                    col_types = adfg_deploy_cols) %>% 
  mutate(DateTagged = parse_datetime(DateTagged,format = "%m/%d/%y")) %>% 
  dplyr::mutate(DateTagged = lubridate::force_tz(DateTagged, 
                                                 'America/Anchorage')) %>% 
  dplyr::mutate(DateTagged = lubridate::as_datetime(DateTagged, 
                                                tz = 'America/Anchorage'))

@@

```{r}
adfg_locations <- readr::read_csv('ADFG_SealLocationData3.csv')
adfg_locations_new <- readr::read_csv('ADFG_SealLocationData_NewRecords.csv')
```

@@

adfg_locations <- readr::read_csv('ADFG_SealLocationData3.csv',
                                  col_types = adfg_locs_cols) %>% 
  dplyr::mutate(Date = as.Date(Date, origin = "1899-12-30", tz ="UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt))

@@

adfg_locations_new <- readr::read_csv('ADFG_SealLocationData_NewRecords.csv',
                                  col_types = adfg_locs_cols) %>% 
  dplyr::mutate(Date = as.Date(Date, origin = "1899-12-30", tz ="UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt))

@@

```{r}
adfg_timeline_cols <- cols(
  .default = readr::col_double(),
  DeployIDs = readr::col_character(),
  TagType = readr::col_character(),
  HistType = readr::col_character(),
  MonthNumb = readr::col_character(),
  LocationQuality = readr::col_character(),
  Sum = readr::col_character()
)

adfg_timelines <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealTimelineData3.csv'),
                                  col_types = adfg_timeline_cols) %>% 
  dplyr::mutate(GMTDate = as.Date(GMTDate, origin = "1899-12-30", 
                                     tz = "UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt),
                TagType = toupper(TagType)) %>% 
  dplyr::rename(speno = DeployIDs,
                tag_family = TagType,
                hist_type = HistType,
                timeline_start_dt = GMTDate) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::left_join(adfg_deployments, by = c("speno","tag_family")) %>% 
  mutate(species_code = case_when(
        species == "bearded" ~ "EB",
        species == "ribbon" ~ "HF",
        species == "spotted" ~ "PL"
    )) %>% 
  mutate(deployid = glue::glue("{species_code}",
                            "{lubridate::year(deploy_dt)}_{ptt}")) %>%
  mutate(unique_day =
             glue::glue("{lubridate::year(timeline_start_dt)}",
                  "{lubridate::yday(timeline_start_dt)}",
                  .sep = "_")) %>%
  dplyr::relocate(deployid) %>% 
  filter(species %in% c('bearded', 'ribbon', 'spotted')) %>%
    filter(lubridate::month(timeline_start_dt) %in% c(3,4,5,6,7)) %>%
  dplyr::select(-c(monthnumb,latitude,longitude,locationquality,sum,hist_type))

>>>>

```{r}
adfg_deployments <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealDeploymentTable3.csv'))
adfg_deployments_new <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealDeploymentTable_NewRecords.csv'))
```

@@

adfg_deployments <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealDeploymentTable3.csv'),
                                    col_types = adfg_deploy_cols) %>% 
  mutate(DateTagged = parse_datetime(DateTagged,format = "%m/%d/%Y %H:%M")) %>% 
  dplyr::mutate(DateTagged = lubridate::force_tz(DateTagged, 
                                                 'America/Anchorage')) %>% 
  dplyr::mutate(DateTagged = lubridate::as_datetime(DateTagged, 
                                                tz = 'America/Anchorage'))

@@

adfg_deployments_new <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealDeploymentTable_NewRecords.csv'),
                                    col_types = adfg_deploy_cols) %>% 
  mutate(DateTagged = parse_datetime(DateTagged,format = "%m/%d/%y")) %>% 
  dplyr::mutate(DateTagged = lubridate::force_tz(DateTagged, 
                                                 'America/Anchorage')) %>% 
  dplyr::mutate(DateTagged = lubridate::as_datetime(DateTagged, 
                                                tz = 'America/Anchorage'))

@@

```{r}
adfg_locations <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealLocationData3.csv'))
adfg_locations_new <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealLocationData_NewRecords.csv'))
```

@@

adfg_locations <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealLocationData3.csv'),
                                  col_types = adfg_locs_cols) %>% 
  dplyr::mutate(Date = as.Date(Date, origin = "1899-12-30", tz ="UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt))

@@

adfg_locations_new <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealLocationData_NewRecords.csv'),
                                  col_types = adfg_locs_cols) %>% 
  dplyr::mutate(Date = as.Date(Date, origin = "1899-12-30", tz ="UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt))

@@

```{r}
adfg_timeline_cols <- cols(
  .default = readr::col_double(),
  DeployIDs = readr::col_character(),
  TagType = readr::col_character(),
  HistType = readr::col_character(),
  GMTDate = readr::col_character(),
  MonthNumb = readr::col_character(),
  LocationQuality = readr::col_character(),
  Sum = readr::col_character()
)

adfg_timelines <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealTimelineData3.csv'),
                                  col_types = adfg_timeline_cols) %>% 
  dplyr::mutate(GMTDate = lubridate::parse_date_time(GMTDate,orders = "mdy"),
                Ptt = as.integer(Ptt),
                TagType = toupper(TagType)) %>% 
  dplyr::rename(speno = DeployIDs,
                tag_family = TagType,
                hist_type = HistType,
                timeline_start_dt = GMTDate) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::left_join(adfg_deployments, by = c("speno","tag_family")) %>% 
  mutate(species_code = case_when(
        species == "bearded" ~ "EB",
        species == "ribbon" ~ "HF",
        species == "spotted" ~ "PL"
    )) %>% 
  mutate(deployid = glue::glue("{species_code}",
                            "{lubridate::year(deploy_dt)}_{ptt}")) %>%
  mutate(unique_day =
             glue::glue("{lubridate::year(timeline_start_dt)}",
                  "{lubridate::yday(timeline_start_dt)}",
                  .sep = "_")) %>%
  dplyr::relocate(deployid) %>% 
  filter(species %in% c('bearded', 'ribbon', 'spotted')) %>%
    filter(lubridate::month(timeline_start_dt) %in% c(3,4,5,6,7)) %>%
  dplyr::select(-c(monthnumb,latitude,longitude,locationquality,sum,hist_type))
